EldersAIR initial med visit data work

### 2021-03-11 elders_health_data_cleaning.Rmd
data cleaning updates

---
title: "Elders health and elder files data cleaning"
author: "Ethan Walker"
date: "Started 28 Feb 2020, Updated 1 March 2021"
output: pdf_document 
---

@@

# Load and merge files from different locations
```{r}
nn_athomelog_initial <- read_xlsx(paste0(file_path, "Input/NN/athomelog.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         adult_id_num = as.character(AdultID),
         area = "NN",
         sampling_visit = as.numeric(SamplingVisit),
         at_home_day = as.factor(Day),
         at_home_7 = as.factor(AtHome1),
         at_home_8 = as.factor(AtHome2),
         at_home_9 = as.factor(AtHome3),
         at_home_10 = as.factor(AtHome4),
         at_home_11 = as.factor(AtHome5),
         at_home_12 = as.factor(AtHome6),
         at_home_13 = as.factor(AtHome7),
         at_home_14 = as.factor(AtHome8),
         at_home_15 = as.factor(AtHome9),
         at_home_16 = as.factor(AtHome10),
         at_home_17 = as.factor(AtHome11),
         at_home_18 = as.factor(AtHome12),
         at_home_19 = as.factor(AtHome13),
         at_home_20 = as.factor(AtHome14),
         at_home_21 = as.factor(AtHome15),
         at_home_22 = as.factor(AtHome16)) %>% 
  select(home_winter_id:at_home_22)

npt_athomelog_initial <- read_xlsx(paste0(file_path, "Input/NP/athomelog.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         adult_id_num = as.character(AdultID),
         area = "NPT",
         sampling_visit = as.numeric(SamplingVisit),
         at_home_day = as.factor(Day),
         at_home_7 = as.factor(AtHome1),
         at_home_8 = as.factor(AtHome2),
         at_home_9 = as.factor(AtHome3),
         at_home_10 = as.factor(AtHome4),
         at_home_11 = as.factor(AtHome5),
         at_home_12 = as.factor(AtHome6),
         at_home_13 = as.factor(AtHome7),
         at_home_14 = as.factor(AtHome8),
         at_home_15 = as.factor(AtHome9),
         at_home_16 = as.factor(AtHome10),
         at_home_17 = as.factor(AtHome11),
         at_home_18 = as.factor(AtHome12),
         at_home_19 = as.factor(AtHome13),
         at_home_20 = as.factor(AtHome14),
         at_home_21 = as.factor(AtHome15),
         at_home_22 = as.factor(AtHome16)) %>% 
  select(home_winter_id:at_home_22)

# Combine logs from all areas
elders_at_home_log <- rbind(nn_athomelog_initial, npt_athomelog_initial) %>% 
  left_join(elders_ids_linked, c("area", "home_winter_id", "adult_id_num"))
# write_rds(elders_at_home_log, "Output/elders_at_home_log.rds")

@@

# Load and merge files from different locations
```{r}
nn_healthhistory_initial <- read_xlsx(paste0(file_path, "Input/NN/healthhistory.xlsx")) %>% 
  rename_all(~str_replace_all(., "Date", "_date")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NN",
         rheum_arth = ra,
         rheum_arth_date = ra_date) %>% 
  select(-id:-homewinterid, -ra, -ra_date, -whatmissing:-ignorereason) %>% 
  select(home_winter_id, adult_id_num, area, rheum_arth, rheum_arth_date,
         lupus:cigarspipes)

npt_healthhistory_initial <- read_xlsx(paste0(file_path, "Input/NP/healthhistory.xlsx")) %>% 
  rename_all(~str_replace_all(., "Date", "_date")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NPT",
         rheum_arth = ra,
         rheum_arth_date = ra_date) %>% 
  select(-id:-homewinterid, -ra, -ra_date, -whatmissing:-ignoremissingdata) %>% 
  select(home_winter_id, adult_id_num, area, rheum_arth, rheum_arth_date,
         lupus:cigarspipes)

# Combine logs from all areas
elders_health_hx <- rbind(nn_healthhistory_initial, npt_healthhistory_initial) %>% 
  left_join(elders_ids_linked, c("area", "home_winter_id", "adult_id_num"))
# write_rds(elders_health_hx, "Output/elders_health_hx.rds")

@@

# Load and merge files from different locations
```{r}
nn_healthextra_initial <- read_xlsx(paste0(file_path, "Input/NN/healthextra.xlsx")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NN",
         sampling_visit = samplingvisit) %>% 
  select( home_winter_id, adult_id_num, sampling_visit, area, cold2m:bronch2mdr)

npt_healthextra_initial <- read_xlsx(paste0(file_path, "Input/NP/healthextra.xlsx")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NPT",
         sampling_visit = samplingvisit) %>% 
  select( home_winter_id, adult_id_num, sampling_visit, area, cold2m:bronch2mdr)

# Combine logs from all areas
elders_health_extra <- rbind(nn_healthextra_initial, npt_healthextra_initial) %>% 
  left_join(elders_ids_linked, c("area", "home_winter_id", "adult_id_num"))
# write_rds(elders_health_extra, "Output/elders_health_extra.rds")

>>>>

---
title: "Elders health and elder files data cleaning"
author: "Ethan Walker"
date: "Started 28 Feb 2020, Updated 10 March 2021"
output: pdf_document 
---

@@

# Load and merge files from different locations
```{r}
nn_athomelog_initial <- read_xlsx(paste0(file_path, "Input/NN/athomelog.xlsx"),
                                   na = "NULL") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         adult_id_num = as.character(AdultID),
         area = "NN",
         sampling_visit = as.numeric(SamplingVisit),
         at_home_day = as.factor(Day),
         "at_home_00:00:00" = as.factor("Yes"),
         "at_home_01:00:00" = as.factor("Yes"),
         "at_home_02:00:00" = as.factor("Yes"),
         "at_home_03:00:00" = as.factor("Yes"),
         "at_home_04:00:00" = as.factor("Yes"),
         "at_home_05:00:00" = as.factor("Yes"),
         "at_home_06:00:00" = as.factor("Yes"),
         "at_home_07:00:00" = as.factor(AtHome1),
         "at_home_08:00:00" = as.factor(AtHome2),
         "at_home_09:00:00" = as.factor(AtHome3),
         "at_home_10:00:00" = as.factor(AtHome4),
         "at_home_11:00:00" = as.factor(AtHome5),
         "at_home_12:00:00" = as.factor(AtHome6),
         "at_home_13:00:00" = as.factor(AtHome7),
         "at_home_14:00:00" = as.factor(AtHome8),
         "at_home_15:00:00" = as.factor(AtHome9),
         "at_home_16:00:00" = as.factor(AtHome10),
         "at_home_17:00:00" = as.factor(AtHome11),
         "at_home_18:00:00" = as.factor(AtHome12),
         "at_home_19:00:00" = as.factor(AtHome13),
         "at_home_20:00:00" = as.factor(AtHome14),
         "at_home_21:00:00" = as.factor(AtHome15),
         "at_home_22:00:00" = as.factor(AtHome16),
         "at_home_23:00:00" = as.factor("Yes")) %>% 
  select(home_winter_id:"at_home_23:00:00")

npt_athomelog_initial <- read_xlsx(paste0(file_path, "Input/NP/athomelog.xlsx"),
                                   na = "NULL") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         adult_id_num = as.character(AdultID),
         area = "NPT",
         sampling_visit = as.numeric(SamplingVisit),
         at_home_day = as.factor(Day),
         "at_home_00:00:00" = as.factor("Yes"),
         "at_home_01:00:00" = as.factor("Yes"),
         "at_home_02:00:00" = as.factor("Yes"),
         "at_home_03:00:00" = as.factor("Yes"),
         "at_home_04:00:00" = as.factor("Yes"),
         "at_home_05:00:00" = as.factor("Yes"),
         "at_home_06:00:00" = as.factor("Yes"),
         "at_home_07:00:00" = as.factor(AtHome1),
         "at_home_08:00:00" = as.factor(AtHome2),
         "at_home_09:00:00" = as.factor(AtHome3),
         "at_home_10:00:00" = as.factor(AtHome4),
         "at_home_11:00:00" = as.factor(AtHome5),
         "at_home_12:00:00" = as.factor(AtHome6),
         "at_home_13:00:00" = as.factor(AtHome7),
         "at_home_14:00:00" = as.factor(AtHome8),
         "at_home_15:00:00" = as.factor(AtHome9),
         "at_home_16:00:00" = as.factor(AtHome10),
         "at_home_17:00:00" = as.factor(AtHome11),
         "at_home_18:00:00" = as.factor(AtHome12),
         "at_home_19:00:00" = as.factor(AtHome13),
         "at_home_20:00:00" = as.factor(AtHome14),
         "at_home_21:00:00" = as.factor(AtHome15),
         "at_home_22:00:00" = as.factor(AtHome16),
         "at_home_23:00:00" = as.factor("Yes")) %>% 
  select(home_winter_id:"at_home_23:00:00")

# Combine logs from all areas
elders_at_home_log <- rbind(nn_athomelog_initial, npt_athomelog_initial) %>% 
  right_join(elders_ids_linked, c("area", "home_winter_id", "adult_id_num")) %>% 
  arrange(area, adult_id_num, winter_id, sampling_visit, at_home_day) %>% 
  group_by(area, adult_id_num, winter_id, sampling_visit, at_home_day) %>% 
  pivot_longer(cols = c("at_home_00:00:00":"at_home_23:00:00"), names_to = "sample_time",
                        values_to = "at_home") %>% 
  ungroup() %>% 
  separate(sample_time, c("trash", "sample_time"), sep = "at_home_", remove = FALSE) %>% 
  select(-trash) %>% 
  mutate(sample_time = as.character(sample_time)) %>% 
  mutate_at(vars(home_winter_id:home), as.factor)

summary(elders_at_home_log)

# write_rds(elders_at_home_log, paste0(file_path, "Output/elders_at_home_log_clean.rds"))

@@

# Load and merge files from different locations
```{r}
nn_healthhistory_initial <- read_xlsx(paste0(file_path, "Input/NN/healthhistory.xlsx"),
                                      na = "NULL") %>% 
  rename_all(~str_replace_all(., "Date", "_date")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NN",
         rheum_arth = ra,
         rheum_arth_date = ra_date) %>% 
  select(-id:-homewinterid, -ra, -ra_date, -whatmissing:-ignorereason) %>% 
  select(adult_id_num, area, rheum_arth, rheum_arth_date,
         lupus:cigarspipes)

npt_healthhistory_initial <- read_xlsx(paste0(file_path, "Input/NP/healthhistory.xlsx"),
                                      na = "NULL") %>% 
  rename_all(~str_replace_all(., "Date", "_date")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NPT",
         rheum_arth = ra,
         rheum_arth_date = ra_date) %>% 
  select(-id:-homewinterid, -ra, -ra_date, -whatmissing:-ignoremissingdata) %>% 
  select(adult_id_num, area, rheum_arth, rheum_arth_date,
         lupus:cigarspipes)

# Combine logs from all areas
elders_health_hx <- rbind(nn_healthhistory_initial, npt_healthhistory_initial) %>% 
  right_join(elders_ids_linked, c("area", "adult_id_num")) %>% 
  select(area, adult_id_num, adult_id_char:treatment, rheum_arth:cigarspipes) %>% 
  arrange(area, adult_id_num, winter_id) %>% 
  mutate_at(vars(area:home), as.factor)

summary(elders_health_hx)

# write_rds(elders_health_hx, paste0(file_path, "Output/elders_health_hx_clean.rds"))

@@

# Load and merge files from different locations
```{r}
nn_healthextra_initial <- read_xlsx(paste0(file_path, "Input/NN/healthextra.xlsx"),
                                      na = "NULL") %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NN",
         sampling_visit = samplingvisit) %>% 
  select( home_winter_id, adult_id_num, sampling_visit, area, cold2m:bronch2mdr)

npt_healthextra_initial <- read_xlsx(paste0(file_path, "Input/NP/healthextra.xlsx"),
                                      na = "NULL") %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NPT",
         sampling_visit = samplingvisit) %>% 
  select( home_winter_id, adult_id_num, sampling_visit, area, cold2m:bronch2mdr)

# Combine logs from all areas
elders_health_extra <- rbind(nn_healthextra_initial, npt_healthextra_initial) %>% 
  right_join(elders_ids_linked, c("area", "home_winter_id", "adult_id_num")) %>% 
  arrange(area, adult_id_num, winter_id, sampling_visit) %>% 
  select(area, adult_id_num, adult_id_char, home, home_id_num, home_winter_id, 
         winter_id, treatment, cold2m:bronch2mdr) %>% 
  mutate_if(is_character, as_factor)

summary(elders_health_extra)

# write_rds(elders_health_extra, paste0(file_path, "Output/elders_health_extra_clean.rds"))

### 2021-03-11 health_history_summary.Rmd
data cleaning updates

---
title: "EldersAIR Health History Summary"
author: "Ethan Walker"
date: "Started 11 March 2020, Updated 12 March 2020"
output: pdf_document
---

@@

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds")) %>% 
  filter(winter_id == 1 | winter_id == 2) %>% 
  arrange(area, adult_id_num)

>>>>

---
title: "EldersAIR Health History Summary"
author: "Ethan Walker"
date: "Started 11 March 2020, Updated 10 March 2021"
output: pdf_document
---

@@

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds"))

### 2021-03-11 medvisit_data_cleaning.Rmd
data cleaning updates

# fix values after check spiro files
npt_medvisit_new2 <- npt_medvisit_new %>% 
  mutate(sp02 = if_else(sp02 < 80, -999, sp02)) %>% 
  mutate(sp02 = if_else(adult_id_num == 58 & sp02 == 80, -999, sp02)) %>% 
  mutate(pr = if_else(adult_id_num == 58 & pr == 80, -999, pr)) %>%
  mutate(bp_sys = if_else(adult_id_num == 58 & bp_sys == 80, -999, bp_sys)) %>%
  replace_with_na_all(condition = ~.x %in% c(-999, 0)) %>% 
  mutate(fvc = if_else(adult_id_num == "47" & fvc == "1.01", 1.81, fvc),
         fev1 = if_else(adult_id_num == "55" & fev1 == "2.98", 1.98, fev1),
         fvc = if_else(adult_id_num == "104" & fvc == "1.2", 1.65, fvc),
         fev1 = if_else(adult_id_num == "104" & fev1 == "1.2", 1.6, fev1),
         fvc_pp = if_else(adult_id_num == "104" & fvc_pp == "42", 58, fvc_pp),
         fev1_pp = if_else(adult_id_num == "104" & fev1_pp == "56", 75, fev1_pp),
         fev1_fvc_ratio = as.numeric(fev1/fvc),
         fev1_fvc_ratio_pp = as.numeric(fev1_pp/fvc_pp))

@@

# fix values after check spiro files
nn_medvisit_new2 <- nn_medvisit_new %>% 
  mutate(bp_dia = if_else(bp_dia < 50, -999, bp_dia)) %>% 
  mutate(sp02 = if_else(sp02 < 80, -999, sp02)) %>% 
  mutate(hr = if_else(hr < 40, -999, hr)) %>% 
  mutate(fev1_fvc_ratio = if_else(fvc == -999, -999, fev1_fvc_ratio)) %>% 
  mutate(fev1_fvc_ratio_pp = if_else(fvc == -999, -999, fev1_fvc_ratio_pp)) %>% 
  replace_with_na_all(condition = ~.x %in% c(-999, 0)) %>% 
  replace_with_na(replace = list(bp_sys = c(9, 80))) %>% 
  mutate(age = if_else(adult_id_num == "47" & age == 17, 71, age)) %>% 
  mutate(fvc = if_else(adult_id_num == "87" & fvc == 2.65, 3.14, fvc),
         fev1 = if_else(adult_id_num == "87" & fev1 == 3.4, 2.65, fev1),
         fvc = if_else(adult_id_num == "77" & fvc == 2.19, 2.95, fvc),
         fev1 = if_else(adult_id_num == "77" & fev1 == 2.72, 2.22, fev1),
         fvc = if_else(adult_id_num == "77" & fvc == 0.81, 2.98, fvc),
         fev1 = if_else(adult_id_num == "77" & fev1 == 0.81, 2.38, fev1),
         fvc_pp = if_else(adult_id_num == "77" & fvc_pp == 57, 76, fvc_pp),
         fev1_pp = if_else(adult_id_num == "77" & fev1_pp == 49, 73, fev1_pp),
         fvc = if_else(adult_id_num == "55" & fvc == 1.13, 1.7, fvc),
         fev1 = if_else(adult_id_num == "55" & fev1 == 1.12, 1.18, fev1),
         fvc_pp = if_else(adult_id_num == "55" & fvc_pp == 0.35, 82, fvc_pp),
         fev1_pp = if_else(adult_id_num == "55" & fev1_pp == 2.31, 77, fev1_pp),
         fvc_pp = if_else(adult_id_num == "77" & fvc_pp == 21, 77, fvc_pp),
         fev1_pp = if_else(adult_id_num == "77" & fev1_pp == 27, 79, fev1_pp),
         fvc = if_else(adult_id_num == "79" & fvc == 1.59, 1.66, fvc),
         fev1 = if_else(adult_id_num == "79" & fev1 == 1.59, 1.19, fev1),
         fvc_pp = if_else(adult_id_num == "79" & fvc_pp == 89, 93, fvc_pp),
         fev1_pp = if_else(adult_id_num == "79" & fev1_pp == 123, 91, fev1_pp),
         fvc = if_else(adult_id_num == "61" & fvc == 3.07, 3.43, fvc),
         fvc_pp = if_else(fvc_pp < 1, fvc_pp*1000, fvc_pp),
         fev1_pp = if_else(fev1_pp < 1, fev1_pp*1000, fev1_pp),
         fvc_pp = if_else(fvc_pp < 10, (fvc/fvc_pp)*100, fvc_pp),
         fev1_pp = if_else(fev1_pp < 10, (fev1/fev1_pp)*100, fev1_pp),
         weight_lbs = if_else(adult_id_num == "61" & weight_lbs == 3.43, 127, weight_lbs),
         height_inches = if_else(height_inches == 5, 60, height_inches),
         height_inches = if_else(height_inches == 79.8, 60, height_inches),
         bp_sys = if_else(adult_id_num == "9" & bp_sys == 94, 104, bp_sys),
         bp_dia = if_else(adult_id_num == "9" & bp_dia == 104, 94, bp_dia),
         fev1_fvc_ratio = as.numeric(fev1/fvc),
         fev1_fvc_ratio_pp = as.numeric(fev1_pp/fvc_pp))

elders_medvisit <- rbind(npt_medvisit_new2, nn_medvisit_new2) %>% 
  select(-gender) %>% 
  mutate(bmi = (weight_lbs/(height_inches^2)*703),
         home_winter_id = as.factor(home_winter_id),
         adult_id_num = as.factor(adult_id_num)) %>% 
  right_join(elders_ids_linked, by = c("area", "home_winter_id", "adult_id_num")) %>% 
  arrange(area, adult_id_num, winter_id, sampling_visit) %>% 
  select(area, home, home_id_num, home_winter_id, winter_id, treatment, 
         adult_id_char, adult_id_num, sampling_visit,
         sp02:weight_lbs, bmi, fvc:spiro_result)

#write_rds(elders_medvisit, paste0(file_path, "Output/elders_medvisit_clean.rds"))

@@

elders_medvisit <- read_rds(paste0(file_path, "Output/elders_medvisit_clean.rds")) %>% 
  mutate(hypertension = if_else(bp_sys >= 140 | bp_dia >= 90, 1, 0),
         hypertension = as.numeric(hypertension),
         obstruction = if_else(fev1_fvc_ratio < 0.7 | fev1_pp < 75, 1, 0),
         obstruction = as.numeric(obstruction))

@@

# Further data checking/cleaning
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")

elders_medvisit <- read_rds(paste0(file_path, "Output/elders_medvisit_clean.rds"))

medvisit_data_checks <- elders_medvisit %>% 
  mutate(bp_check = if_else(bp_dia >= bp_sys, 1, 0), # no instances of dbp >= sbp
         hr_check = if_else(pr-hr >= abs(10), 1, 0), # 53 instances of pr/hr diff >= 10
         fvc_check = if_else(fev1 >= fvc, 1, 0)) %>% # 2 instances of fvc = fev1; none where fev1 > fvc
  filter(fvc_check == 1)

@@

>>>>

# fix values after check spiro files
npt_medvisit_new2 <- npt_medvisit_new %>% 
  #mutate(sp02 = if_else(sp02 < 80, -999, sp02)) %>% 
  mutate(sp02 = if_else(adult_id_num == 58 & sp02 == 80, -999, sp02)) %>% 
  mutate(pr = if_else(adult_id_num == 58 & pr == 80, -999, pr)) %>%
  mutate(bp_sys = if_else(adult_id_num == 58 & bp_sys == 80, -999, bp_sys)) %>%
  replace_with_na_all(condition = ~.x %in% c(-999, 0)) %>% 
  mutate(fvc = if_else(adult_id_num == "47" & fvc == "1.01", 1.81, fvc),
         fev1 = if_else(adult_id_num == "55" & fev1 == "2.98", 1.98, fev1),
         fvc = if_else(adult_id_num == "104" & fvc == "1.2", 1.65, fvc),
         fev1 = if_else(adult_id_num == "104" & fev1 == "1.2", 1.6, fev1),
         fvc_pp = if_else(adult_id_num == "104" & fvc_pp == "42", 58, fvc_pp),
         fev1_pp = if_else(adult_id_num == "104" & fev1_pp == "56", 75, fev1_pp),
         fev1_fvc_ratio = as.numeric(fev1/fvc),
         fev1_fvc_ratio_pp = as.numeric(fev1_pp/fvc_pp))

@@

# fix values after check spiro files
nn_medvisit_new2 <- nn_medvisit_new %>% 
  #mutate(bp_dia = if_else(bp_dia < 50, -999, bp_dia)) %>% 
  #mutate(sp02 = if_else(sp02 < 80, -999, sp02)) %>% 
  #mutate(hr = if_else(hr < 40, -999, hr)) %>% 
  mutate(fev1_fvc_ratio = if_else(fvc == -999, -999, fev1_fvc_ratio)) %>% 
  mutate(fev1_fvc_ratio_pp = if_else(fvc == -999, -999, fev1_fvc_ratio_pp)) %>% 
  replace_with_na_all(condition = ~.x %in% c(-999, 0)) %>% 
  replace_with_na(replace = list(bp_sys = c(9, 80))) %>% 
  mutate(age = if_else(adult_id_num == "47" & age == 17, 71, age)) %>% 
  mutate(fvc = if_else(adult_id_num == "87" & fvc == 2.65, 3.14, fvc),
         fev1 = if_else(adult_id_num == "87" & fev1 == 3.4, 2.65, fev1),
         fvc = if_else(adult_id_num == "77" & fvc == 2.19, 2.95, fvc),
         fev1 = if_else(adult_id_num == "77" & fev1 == 2.72, 2.22, fev1),
         fvc = if_else(adult_id_num == "77" & fvc == 0.81, 2.98, fvc),
         fev1 = if_else(adult_id_num == "77" & fev1 == 0.81, 2.38, fev1),
         fvc_pp = if_else(adult_id_num == "77" & fvc_pp == 57, 76, fvc_pp),
         fev1_pp = if_else(adult_id_num == "77" & fev1_pp == 49, 73, fev1_pp),
         fvc = if_else(adult_id_num == "55" & fvc == 1.13, 1.7, fvc),
         fev1 = if_else(adult_id_num == "55" & fev1 == 1.12, 1.18, fev1),
         fvc_pp = if_else(adult_id_num == "55" & fvc_pp == 0.35, 82, fvc_pp),
         fev1_pp = if_else(adult_id_num == "55" & fev1_pp == 2.31, 77, fev1_pp),
         fvc_pp = if_else(adult_id_num == "77" & fvc_pp == 21, 77, fvc_pp),
         fev1_pp = if_else(adult_id_num == "77" & fev1_pp == 27, 79, fev1_pp),
         fvc = if_else(adult_id_num == "79" & fvc == 1.59, 1.66, fvc),
         fev1 = if_else(adult_id_num == "79" & fev1 == 1.59, 1.19, fev1),
         fvc_pp = if_else(adult_id_num == "79" & fvc_pp == 89, 93, fvc_pp),
         fev1_pp = if_else(adult_id_num == "79" & fev1_pp == 123, 91, fev1_pp),
         fvc = if_else(adult_id_num == "61" & fvc == 3.07, 3.43, fvc),
         fvc_pp = if_else(fvc_pp < 1, fvc_pp*1000, fvc_pp),
         fev1_pp = if_else(fev1_pp < 1, fev1_pp*1000, fev1_pp),
         fvc_pp = if_else(fvc_pp < 10, (fvc/fvc_pp)*100, fvc_pp),
         fev1_pp = if_else(fev1_pp < 10, (fev1/fev1_pp)*100, fev1_pp),
         weight_lbs = if_else(adult_id_num == "61" & weight_lbs == 3.43, 127, weight_lbs),
         height_inches = if_else(height_inches == 5, 60, height_inches),
         height_inches = if_else(height_inches == 79.8, 60, height_inches),
         bp_sys = if_else(adult_id_num == "9" & bp_sys == 94, 104, bp_sys),
         bp_dia = if_else(adult_id_num == "9" & bp_dia == 104, 94, bp_dia),
         fev1_fvc_ratio = as.numeric(fev1/fvc),
         fev1_fvc_ratio_pp = as.numeric(fev1_pp/fvc_pp))

elders_medvisit <- rbind(npt_medvisit_new2, nn_medvisit_new2) %>% 
  #select(-gender) %>% 
  mutate(bmi = (weight_lbs/(height_inches^2)*703),
         home_winter_id = as.factor(home_winter_id),
         adult_id_num = as.factor(adult_id_num)) %>% 
  right_join(elders_ids_linked, by = c("area", "home_winter_id", "adult_id_num")) %>% 
  arrange(area, adult_id_num, winter_id, sampling_visit) %>% 
  select(area, home, home_id_num, home_winter_id, winter_id, treatment, 
         adult_id_char, adult_id_num, sampling_visit,
         sp02:weight_lbs, bmi, fvc:spiro_result)

write_rds(elders_medvisit, paste0(file_path, "Output/elders_medvisit_initial.rds"))

@@

elders_medvisit <- read_rds(paste0(file_path, "Output/elders_medvisit_initial.rds")) %>% 
  mutate(hypertension = if_else(bp_sys >= 140 | bp_dia >= 90, 1, 0),
         hypertension = as.numeric(hypertension),
         obstruction = if_else(fev1_fvc_ratio < 0.7 | fev1_pp < 75, 1, 0),
         obstruction = as.numeric(obstruction))

@@

# Further data checking
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")

elders_medvisit <- read_rds(paste0(file_path, "Output/elders_medvisit_initial.rds"))

summary(elders_medvisit)

medvisit_data_checks <- elders_medvisit %>% 
  mutate(bp_check = if_else(bp_dia >= bp_sys, 1, 0), # no instances of dbp >= sbp
         hr_check = if_else(pr-hr >= abs(10), 1, 0), # 53 instances of pr/hr diff >= 10
         fvc_check = if_else(fev1 >= fvc, 1, 0)) %>% # 2 instances of fvc = fev1; none where fev1 > fvc
  filter(bp_check == 1)

@@

# Clean up for final dataset
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")

elders_medvisit <- read_rds(paste0(file_path, "Output/elders_medvisit_initial.rds"))

elders_medvisit_clean <- elders_medvisit %>% 
  mutate_if(is_character, as_factor) %>% 
  mutate(sampling_visit = as.factor(sampling_visit)) %>% 
  mutate(stage_2_htn = if_else(bp_sys >= 140 | bp_dia >= 90, "Yes", "No"),
         stage_2_htn = as.factor(stage_2_htn),
         fev1_fvc_ratio_0.7 = if_else(fev1_fvc_ratio < 0.7, "Yes", "No"),
         fev1_fvc_ratio_0.7 = as.factor(fev1_fvc_ratio_0.7),
         spiro_grade = factor(spiro_grade, levels = c("A", "B", "C", "D", "F")),
         spiro_result = factor(spiro_result, levels = c("Normal", "Restrictive", 
                                                        "Obstructive", "Both")))

data_check <- elders_medvisit_clean %>% 
  filter(sp02 < 80 | pr < 50 | bp_sys < 90 | bp_dia < 40 | hr < 50) %>% 
  arrange(area, home, winter_id, sampling_visit)

# write_csv(data_check, paste0(file_path, "Output/elders_medvisit_check.csv"))

#summary(elders_medvisit_clean)

write_rds(elders_medvisit_clean, paste0(file_path, "Output/elders_medvisit_clean.rds"))
```
